\begin{thebibliography}{1}

\bibitem{han2007frequent}
Han, Jiawei, et al. "Frequent pattern mining: current status and future directions." Data Mining and Knowledge Discovery 15.1 (2007): 55-86.

\bibitem{unknownbook}
I could not find the book on google scholar, thus I provide the link to the chapter for now.

\bibitem{predictCritical}
Chen, Jun, and Ratnesh Kumar. "Pattern Mining for Predicting Critical Events from Sequential Event Data Log." WODES. 2014.

\bibitem{anomaly}
Sureka, Ashish. "Kernel Based Sequential Data Anomaly Detection in Business Process Event Logs." arXiv preprint arXiv:1507.01168 (2015).

\bibitem{logcluster}
Vaarandi, Risto, and Mauno Pihelgas. "LogCluster-A Data Clustering and Pattern Mining Algorithm for Event Logs." Network and Service Management (CNSM), 2015 11th International Conference on. IEEE, 2015.

\bibitem{processMining}
Priyadharshini, V., and A. Malathi. "Analysis of Process Mining Model for Software Reliability Dataset using HMM." Indian Journal of Science and Technology 9.4 (2016).

\bibitem{fastFrequentPattern}
Lin, Kawuu W., Sheng-Hao Chung, and Chun-Cheng Lin. "A fast and distributed algorithm for mining frequent patterns in congested networks." Computing (2015): 1-22.

\bibitem{dsms}
Motwani, Rajeev, et al. "Query processing, resource management, and approximation in a data stream management system." CIDR, 2003.

\bibitem{approxfreq}
Manku, Gurmeet Singh, and Rajeev Motwani. "Approximate frequency counts over data streams." Proceedings of the 28th international conference on Very Large Data Bases. VLDB Endowment, 2002.

\bibitem{generatingDiverse}
Zimmermann, Armin. "Generating diverse realistic data sets for episode mining." Data Mining Workshops (ICDMW), 2012 IEEE 12th International Conference on. IEEE, 2012.

\bibitem{closedEpisodeMining}
Zhou, Wenzhi, Hongyan Liu, and Hong Cheng. "Mining closed episodes from event sequences efficiently." Advances in Knowledge Discovery and Data Mining. Springer Berlin Heidelberg, 2010. 310-318.

\bibitem{sequentialPatternMining}
Slimani, Thabet, and Amor Lazzez. "Sequential mining: Patterns and algorithms analysis." arXiv preprint arXiv:1311.0350 (2013).

\bibitem{generatingEpisodeDatasets}
Zimmermann, Armin. "Generating diverse realistic data sets for episode mining." Data Mining Workshops (ICDMW), 2012 IEEE 12th International Conference on. IEEE, 2012.

\bibitem{sequentialPatternMining2}
Zhao, Qiankun, and Sourav S. Bhowmick. "Sequential pattern mining: A survey." ITechnical Report CAIS Nayang Technological University Singapore (2003): 1-26.

\bibitem{fastEpisodeMining}
Laxman, Srivatsan, P. S. Sastry, and K. P. Unnikrishnan. "A fast algorithm for finding frequent episodes in event streams." Proceedings of the 13th ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2007.

\end{thebibliography}